What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-30 paper/main.tex
update graphs, citations, and descriptions

\documentclass[preprint,12pt]{elsarticle}
\journal{Journal of Computer Languages}

\usepackage{amsmath, amssymb, amsthm,tikz, subfig}
\usetikzlibrary{positioning,shapes,quotes,calc}

@@

\subsection{Timeline}
We present timelines as graphic visualizations. It contains the following features:
\begin{itemize}
    \item Every timeline starts with a node named ``start''.
    \item Every node represents one time step, and each node has a propositional logic formula $\Psi$, which specifies the behavior of atomic propositions at that time step. The formula $\Psi$ must be true at that time step. If $\Psi = 1$, that means all atomic propositions can behave arbitrarily.
    \item A node with label ``$\cdots$'' means to repeat the node prior to it and after it finitely many times.
    \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its starting point.
\end{itemize}

@@

\begin{example}
    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by two nodes with $\lnot a$ separated by $\cdots$ (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $1$ (true) in the grey box.
    \begin{figure}[!h]
        \centering
        \begin{tikzpicture}
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!start\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) [right= 0.75cm of s] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [right= 0.75cm of a1] {\!\!\!$\dots$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$a$\!\!\!};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.25cm}] (g) [right= 0.6cm of a4] {};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$1$\!\!\!};
        \draw[thick, line width=1.25] (s) edge[-latex] (a1) (a1) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5);

        \end{tikzpicture}
    %    \includegraphics[scale=0.4]{examples/ex15/ex15.png}
        \caption{Example timeline for specification ``$a$ is eventually true''}
        \label{fig:ex15}
    \end{figure}
\end{example}

@@

\begin{example}
    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
    \begin{figure}[h!]
        \centering
                \resizebox{\textwidth}{!}{
        \begin{tikzpicture}
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
        \node (m) at ($(a1)!0.5!(a2)$) {};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 12.5cm of m] {\!\!\!start\!\!\!};

        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a7) [left= .75cm of a1] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a8) [left= .75cm of a2] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a9) [left= .75cm of a8] {\!\!\!$a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a10) [left= .75cm of a9] {\!\!\!$\dots$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a11) [left= .75cm of a10] {\!\!\!$a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a12) [left= .75cm of a11] {\!\!\!$a$\!\!\!};

        \draw[thick, line width=1.25] (s) edge[-latex] (a12) (s) edge[-latex] (a7) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
        \draw[thick, line width=1.25] (a12) edge[-latex] (a11) (a11) edge[-latex] (a10) (a10) edge[-latex] (a9) (a9) edge[-latex] (a8) (a8) edge[-latex] (a1) (a8) edge[-latex] (a2) (a7) edge[-latex] (a1) (a7) edge[-latex] (a2);

        \end{tikzpicture}}
%        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
        \caption{Timeline for %un-simplified 
        $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
        \label{fig:unsimplified}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \resizebox{.8\textwidth}{!}{
        \begin{tikzpicture}
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
  %      \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
        \node (m) at ($(a1)!0.5!(a2)$) {};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 2cm of m] {\!\!\!start\!\!\!};
        \draw[thick, line width=1.25] (s) edge[-latex] (a1) (s) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
        \end{tikzpicture}}
  %      \includegraphics[scale=0.3]{examples/ex9/ex9.png}
        \caption{Timeline for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
        \label{fig:simplified}
    \end{figure}
\end{example}

>>>>

\documentclass[preprint,12pt]{elsarticle}
\journal{Journal of Computer Languages}
\usepackage[x11names, svgnames, rgb]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm,tikz, subfig}
\usetikzlibrary{positioning,shapes,quotes,calc,snakes,arrows}

@@

\subsection{Timeline}
We present timelines as graphic visualizations. It contains the following features:
\begin{itemize}
    \item Every timeline starts with a node named ``start''.
    \item Every node represents one time step, and each node has a propositional logic formula $\Psi$, which specifies the behavior of atomic propositions at that time step. The formula $\Psi$ must be true at that time step. If $\Psi = 1$, that means all atomic propositions can behave arbitrarily.
    \item A node in egg shake with a caption ``repeats $0$ - $\infty$'' means to repeat the (one time step) current node for arbitrarily finitely many times.
    \item A node with label ``$\cdots$'' means to repeat the pattern prior to it and after it arbitrarily finitely many times.
    \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its starting point.
\end{itemize}

@@

\begin{example}
    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by the second node (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $\top$ (true) in the grey box.
    \begin{figure}[!h]
        \centering
        \begin{tikzpicture}[>=latex',line join=bevel,]
            \pgfsetlinewidth{1bp}
          %%
          \begin{scope}
            \pgfsetstrokecolor{black}
            \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
            \pgfsetstrokecolor{strokecol}
            \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
            \pgfsetfillcolor{fillcol}
            \filldraw (287.84bp,8.0bp) -- (287.84bp,60.0bp) -- (357.84bp,60.0bp) -- (357.84bp,8.0bp) -- cycle;
          \end{scope}
            \pgfsetcolor{black}
            % Edge: start -> 0
            \draw [->] (54.252bp,34.0bp) .. controls (61.968bp,34.0bp) and (70.673bp,34.0bp)  .. (90.636bp,34.0bp);
            % Edge: 0 -> 1
            \draw [->] (169.36bp,34.0bp) .. controls (177.45bp,34.0bp) and (185.97bp,34.0bp)  .. (205.41bp,34.0bp);
            % Edge: 1 -> 2
            \draw [->] (260.25bp,34.0bp) .. controls (267.73bp,34.0bp) and (276.03bp,34.0bp)  .. (295.46bp,34.0bp);
            % Node: 2
          \begin{scope}
            \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
            \pgfsetstrokecolor{strokecol}
            \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
            \pgfsetfillcolor{fillcol}
            \filldraw [opacity=1] (322.84bp,34.0bp) ellipse (27.0bp and 18.0bp);
            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
            \pgfsetstrokecolor{strokecol}
            \draw (322.84bp,34.0bp) node {$\top$};
          \end{scope}
            % Node: start
          \begin{scope}
            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
            \pgfsetstrokecolor{strokecol}
            \draw (27.0bp,34.0bp) ellipse (27.0bp and 18.0bp);
            \draw (27.0bp,34.0bp) node {start};
          \end{scope}
            % Node: 0
          \begin{scope}
            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
            \pgfsetstrokecolor{strokecol}
            \draw (133.61bp,16.05bp) -- (136.05bp,16.15bp) -- (138.47bp,16.3bp) -- (140.85bp,16.49bp) -- (143.18bp,16.74bp) -- (145.46bp,17.03bp) -- (147.68bp,17.36bp) -- (149.83bp,17.75bp) -- (151.9bp,18.18bp) -- (153.88bp,18.65bp) -- (155.76bp,19.16bp) -- (157.54bp,19.71bp) -- (159.22bp,20.31bp) -- (160.78bp,20.94bp) -- (162.23bp,21.61bp) -- (163.56bp,22.31bp) -- (164.76bp,23.04bp) -- (165.83bp,23.8bp) -- (166.78bp,24.59bp) -- (167.59bp,25.41bp) -- (168.28bp,26.25bp) -- (168.83bp,27.11bp) -- (169.25bp,27.99bp) -- (169.55bp,28.89bp) -- (169.72bp,29.8bp) -- (169.76bp,30.72bp) -- (169.69bp,31.65bp) -- (169.5bp,32.59bp) -- (169.19bp,33.53bp) -- (168.77bp,34.47bp) -- (168.25bp,35.41bp) -- (167.63bp,36.35bp) -- (166.92bp,37.28bp) -- (166.11bp,38.2bp) -- (165.22bp,39.11bp) -- (164.26bp,40.01bp) -- (163.21bp,40.89bp) -- (162.1bp,41.75bp) -- (160.93bp,42.59bp) -- (159.7bp,43.41bp) -- (158.42bp,44.2bp) -- (157.09bp,44.96bp) -- (155.71bp,45.69bp) -- (154.3bp,46.39bp) -- (152.85bp,47.06bp) -- (151.38bp,47.69bp) -- (149.87bp,48.29bp) -- (148.35bp,48.84bp) -- (146.8bp,49.35bp) -- (145.24bp,49.82bp) -- (143.66bp,50.25bp) -- (142.07bp,50.64bp) -- (140.47bp,50.97bp) -- (138.86bp,51.26bp) -- (137.24bp,51.51bp) -- (135.62bp,51.7bp) -- (133.99bp,51.85bp) -- (132.37bp,51.95bp) -- (130.74bp,52.0bp) -- (129.11bp,52.0bp) -- (127.48bp,51.95bp) -- (125.85bp,51.85bp) -- (124.22bp,51.7bp) -- (122.6bp,51.51bp) -- (120.99bp,51.26bp) -- (119.38bp,50.97bp) -- (117.78bp,50.64bp) -- (116.19bp,50.25bp) -- (114.61bp,49.82bp) -- (113.04bp,49.35bp) -- (111.5bp,48.84bp) -- (109.97bp,48.29bp) -- (108.47bp,47.69bp) -- (106.99bp,47.06bp) -- (105.54bp,46.39bp) -- (104.13bp,45.69bp) -- (102.76bp,44.96bp) -- (101.43bp,44.2bp) -- (100.14bp,43.41bp) -- (98.91bp,42.59bp) -- (97.74bp,41.75bp) -- (96.63bp,40.89bp) -- (95.59bp,40.01bp) -- (94.62bp,39.11bp) -- (93.73bp,38.2bp) -- (92.92bp,37.28bp) -- (92.21bp,36.35bp) -- (91.59bp,35.41bp) -- (91.07bp,34.47bp) -- (90.65bp,33.53bp) -- (90.35bp,32.59bp) -- (90.15bp,31.65bp) -- (90.08bp,30.72bp) -- (90.12bp,29.8bp) -- (90.29bp,28.89bp) -- (90.59bp,27.99bp) -- (91.01bp,27.11bp) -- (91.57bp,26.25bp) -- (92.25bp,25.41bp) -- (93.07bp,24.59bp) -- (94.01bp,23.8bp) -- (95.09bp,23.04bp) -- (96.29bp,22.31bp) -- (97.61bp,21.61bp) -- (99.06bp,20.94bp) -- (100.62bp,20.31bp) -- (102.3bp,19.71bp) -- (104.08bp,19.16bp) -- (105.97bp,18.65bp) -- (107.95bp,18.18bp) -- (110.01bp,17.75bp) -- (112.16bp,17.36bp) -- (114.38bp,17.03bp) -- (116.66bp,16.74bp) -- (119.0bp,16.49bp) -- (121.38bp,16.3bp) -- (123.79bp,16.15bp) -- (126.23bp,16.05bp) -- (128.69bp,16.0bp) -- (131.15bp,16.0bp) -- cycle;
            \draw (129.92bp,34.0bp) node [align=center] {$\neg \text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
          \end{scope}
            % Node: 1
          \begin{scope}
            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
            \pgfsetstrokecolor{strokecol}
            \draw (232.84bp,34.0bp) ellipse (27.0bp and 18.0bp);
            \draw (232.84bp,34.0bp) node {$\text{a}$};
          \end{scope}
          %
          \end{tikzpicture}
    %    \includegraphics[scale=0.4]{examples/ex15/ex15.png}
        \caption{Example timeline for specification ``$a$ is eventually true''}
        \label{fig:ex15}
    \end{figure}
\end{example}

@@

\begin{example}
    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
    \begin{figure}[h!]
        \centering
                \resizebox{\textwidth}{!}{
                    \begin{tikzpicture}[>=latex',line join=bevel,]
                        \pgfsetlinewidth{1bp}
                      %%
                      \begin{scope}
                        \pgfsetstrokecolor{black}
                        \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
                        \pgfsetstrokecolor{strokecol}
                        \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
                        \pgfsetfillcolor{fillcol}
                        \filldraw (371.46bp,8.0bp) -- (371.46bp,114.0bp) -- (640.91bp,114.0bp) -- (640.91bp,8.0bp) -- cycle;
                      \end{scope}
                        \pgfsetcolor{black}
                        % Edge: 5 -> 6
                        \draw [->] (433.9bp,34.0bp) .. controls (441.44bp,34.0bp) and (449.89bp,34.0bp)  .. (469.54bp,34.0bp);
                        % Edge: 6 -> 7
                        \draw [->] (542.74bp,34.0bp) .. controls (550.66bp,34.0bp) and (559.09bp,34.0bp)  .. (578.42bp,34.0bp);
                        % Edge: start -> 0
                        \draw [->] (54.272bp,65.285bp) .. controls (105.49bp,69.739bp) and (218.83bp,79.597bp)  .. (289.35bp,85.729bp);
                        % Edge: start -> 1
                        \draw [->] (52.513bp,56.593bp) .. controls (61.118bp,54.344bp) and (70.969bp,51.769bp)  .. (91.313bp,46.452bp);
                        % Edge: 0 -> 4
                        \draw [->] (343.86bp,88.0bp) .. controls (351.34bp,88.0bp) and (359.64bp,88.0bp)  .. (379.07bp,88.0bp);
                        % Edge: 0 -> 5
                        \draw [->] (336.99bp,76.016bp) .. controls (348.61bp,68.885bp) and (363.57bp,59.705bp)  .. (385.98bp,45.951bp);
                        % Edge: 1 -> 2
                        \draw [->] (144.45bp,39.459bp) .. controls (152.06bp,39.303bp) and (160.61bp,39.128bp)  .. (180.45bp,38.722bp);
                        % Edge: 2 -> 3
                        \draw [->] (253.84bp,36.522bp) .. controls (261.64bp,36.203bp) and (269.9bp,35.864bp)  .. (289.26bp,35.072bp);
                        % Edge: 3 -> 4
                        \draw [->] (336.99bp,45.984bp) .. controls (348.61bp,53.115bp) and (363.57bp,62.295bp)  .. (385.98bp,76.049bp);
                        % Edge: 3 -> 5
                        \draw [->] (343.86bp,34.0bp) .. controls (351.34bp,34.0bp) and (359.64bp,34.0bp)  .. (379.07bp,34.0bp);
                        % Node: 4
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
                        \pgfsetstrokecolor{strokecol}
                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
                        \pgfsetfillcolor{fillcol}
                        \filldraw [opacity=1] (406.46bp,88.0bp) ellipse (27.0bp and 18.0bp);
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (406.46bp,88.0bp) node {$\neg \text{a}$};
                      \end{scope}
                        % Node: 5
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
                        \pgfsetstrokecolor{strokecol}
                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
                        \pgfsetfillcolor{fillcol}
                        \filldraw [opacity=1] (406.46bp,34.0bp) ellipse (27.0bp and 18.0bp);
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (406.46bp,34.0bp) node {$\text{a}$};
                      \end{scope}
                        % Node: 6
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
                        \pgfsetstrokecolor{strokecol}
                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
                        \pgfsetfillcolor{fillcol}
                        \filldraw (509.6bp,16.05bp) -- (511.87bp,16.15bp) -- (514.11bp,16.3bp) -- (516.32bp,16.49bp) -- (518.48bp,16.74bp) -- (520.6bp,17.03bp) -- (522.66bp,17.36bp) -- (524.65bp,17.75bp) -- (526.57bp,18.18bp) -- (528.4bp,18.65bp) -- (530.15bp,19.16bp) -- (531.8bp,19.71bp) -- (533.36bp,20.31bp) -- (534.81bp,20.94bp) -- (536.15bp,21.61bp) -- (537.38bp,22.31bp) -- (538.5bp,23.04bp) -- (539.49bp,23.8bp) -- (540.37bp,24.59bp) -- (541.12bp,25.41bp) -- (541.76bp,26.25bp) -- (542.27bp,27.11bp) -- (542.67bp,27.99bp) -- (542.94bp,28.89bp) -- (543.1bp,29.8bp) -- (543.14bp,30.72bp) -- (543.07bp,31.65bp) -- (542.89bp,32.59bp) -- (542.61bp,33.53bp) -- (542.22bp,34.47bp) -- (541.74bp,35.41bp) -- (541.16bp,36.35bp) -- (540.5bp,37.28bp) -- (539.75bp,38.2bp) -- (538.93bp,39.11bp) -- (538.03bp,40.01bp) -- (537.06bp,40.89bp) -- (536.03bp,41.75bp) -- (534.95bp,42.59bp) -- (533.8bp,43.41bp) -- (532.61bp,44.2bp) -- (531.38bp,44.96bp) -- (530.11bp,45.69bp) -- (528.8bp,46.39bp) -- (527.45bp,47.06bp) -- (526.08bp,47.69bp) -- (524.69bp,48.29bp) -- (523.27bp,48.84bp) -- (521.84bp,49.35bp) -- (520.39bp,49.82bp) -- (518.92bp,50.25bp) -- (517.45bp,50.64bp) -- (515.96bp,50.97bp) -- (514.47bp,51.26bp) -- (512.97bp,51.51bp) -- (511.47bp,51.7bp) -- (509.96bp,51.85bp) -- (508.45bp,51.95bp) -- (506.94bp,52.0bp) -- (505.43bp,52.0bp) -- (503.92bp,51.95bp) -- (502.41bp,51.85bp) -- (500.9bp,51.7bp) -- (499.39bp,51.51bp) -- (497.9bp,51.26bp) -- (496.4bp,50.97bp) -- (494.92bp,50.64bp) -- (493.44bp,50.25bp) -- (491.98bp,49.82bp) -- (490.53bp,49.35bp) -- (489.09bp,48.84bp) -- (487.68bp,48.29bp) -- (486.28bp,47.69bp) -- (484.91bp,47.06bp) -- (483.57bp,46.39bp) -- (482.26bp,45.69bp) -- (480.99bp,44.96bp) -- (479.75bp,44.2bp) -- (478.56bp,43.41bp) -- (477.42bp,42.59bp) -- (476.33bp,41.75bp) -- (475.3bp,40.89bp) -- (474.34bp,40.01bp) -- (473.44bp,39.11bp) -- (472.61bp,38.2bp) -- (471.87bp,37.28bp) -- (471.2bp,36.35bp) -- (470.63bp,35.41bp) -- (470.14bp,34.47bp) -- (469.76bp,33.53bp) -- (469.47bp,32.59bp) -- (469.3bp,31.65bp) -- (469.23bp,30.72bp) -- (469.27bp,29.8bp) -- (469.43bp,28.89bp) -- (469.7bp,27.99bp) -- (470.09bp,27.11bp) -- (470.61bp,26.25bp) -- (471.24bp,25.41bp) -- (472.0bp,24.59bp) -- (472.88bp,23.8bp) -- (473.87bp,23.04bp) -- (474.99bp,22.31bp) -- (476.21bp,21.61bp) -- (477.56bp,20.94bp) -- (479.01bp,20.31bp) -- (480.56bp,19.71bp) -- (482.22bp,19.16bp) -- (483.96bp,18.65bp) -- (485.8bp,18.18bp) -- (487.72bp,17.75bp) -- (489.71bp,17.36bp) -- (491.77bp,17.03bp) -- (493.88bp,16.74bp) -- (496.05bp,16.49bp) -- (498.26bp,16.3bp) -- (500.5bp,16.15bp) -- (502.76bp,16.05bp) -- (505.04bp,16.0bp) -- (507.32bp,16.0bp) -- cycle;
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (506.18bp,34.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
                      \end{scope}
                        % Node: 7
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
                        \pgfsetstrokecolor{strokecol}
                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
                        \pgfsetfillcolor{fillcol}
                        \filldraw [opacity=1] (605.91bp,34.0bp) ellipse (27.0bp and 18.0bp);
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (605.91bp,34.0bp) node {$\neg \text{a}$};
                      \end{scope}
                        % Node: start
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (27.0bp,63.0bp) ellipse (27.0bp and 18.0bp);
                        \draw (27.0bp,63.0bp) node {start};
                      \end{scope}
                        % Node: 0
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (316.46bp,88.0bp) ellipse (27.0bp and 18.0bp);
                        \draw (316.46bp,88.0bp) node {$\neg \text{a}$};
                      \end{scope}
                        % Node: 1
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (117.0bp,40.0bp) ellipse (27.0bp and 18.0bp);
                        \draw (117.0bp,40.0bp) node {$\text{a}$};
                      \end{scope}
                        % Node: 2
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (220.15bp,20.05bp) -- (222.41bp,20.15bp) -- (224.65bp,20.3bp) -- (226.86bp,20.49bp) -- (229.03bp,20.74bp) -- (231.14bp,21.03bp) -- (233.2bp,21.36bp) -- (235.19bp,21.75bp) -- (237.11bp,22.18bp) -- (238.95bp,22.65bp) -- (240.7bp,23.16bp) -- (242.35bp,23.71bp) -- (243.9bp,24.31bp) -- (245.35bp,24.94bp) -- (246.7bp,25.61bp) -- (247.93bp,26.31bp) -- (249.04bp,27.04bp) -- (250.04bp,27.8bp) -- (250.91bp,28.59bp) -- (251.67bp,29.41bp) -- (252.3bp,30.25bp) -- (252.82bp,31.11bp) -- (253.21bp,31.99bp) -- (253.49bp,32.89bp) -- (253.64bp,33.8bp) -- (253.68bp,34.72bp) -- (253.61bp,35.65bp) -- (253.44bp,36.59bp) -- (253.15bp,37.53bp) -- (252.77bp,38.47bp) -- (252.28bp,39.41bp) -- (251.71bp,40.35bp) -- (251.04bp,41.28bp) -- (250.3bp,42.2bp) -- (249.47bp,43.11bp) -- (248.57bp,44.01bp) -- (247.61bp,44.89bp) -- (246.58bp,45.75bp) -- (245.49bp,46.59bp) -- (244.35bp,47.41bp) -- (243.16bp,48.2bp) -- (241.92bp,48.96bp) -- (240.65bp,49.69bp) -- (239.34bp,50.39bp) -- (238.0bp,51.06bp) -- (236.63bp,51.69bp) -- (235.23bp,52.29bp) -- (233.82bp,52.84bp) -- (232.38bp,53.35bp) -- (230.93bp,53.82bp) -- (229.47bp,54.25bp) -- (227.99bp,54.64bp) -- (226.51bp,54.97bp) -- (225.02bp,55.26bp) -- (223.52bp,55.51bp) -- (222.01bp,55.7bp) -- (220.51bp,55.85bp) -- (219.0bp,55.95bp) -- (217.48bp,56.0bp) -- (215.97bp,56.0bp) -- (214.46bp,55.95bp) -- (212.95bp,55.85bp) -- (211.44bp,55.7bp) -- (209.94bp,55.51bp) -- (208.44bp,55.26bp) -- (206.95bp,54.97bp) -- (205.46bp,54.64bp) -- (203.99bp,54.25bp) -- (202.52bp,53.82bp) -- (201.07bp,53.35bp) -- (199.64bp,52.84bp) -- (198.22bp,52.29bp) -- (196.83bp,51.69bp) -- (195.46bp,51.06bp) -- (194.12bp,50.39bp) -- (192.81bp,49.69bp) -- (191.53bp,48.96bp) -- (190.3bp,48.2bp) -- (189.11bp,47.41bp) -- (187.97bp,46.59bp) -- (186.88bp,45.75bp) -- (185.85bp,44.89bp) -- (184.88bp,44.01bp) -- (183.98bp,43.11bp) -- (183.16bp,42.2bp) -- (182.41bp,41.28bp) -- (181.75bp,40.35bp) -- (181.17bp,39.41bp) -- (180.69bp,38.47bp) -- (180.3bp,37.53bp) -- (180.02bp,36.59bp) -- (179.84bp,35.65bp) -- (179.77bp,34.72bp) -- (179.81bp,33.8bp) -- (179.97bp,32.89bp) -- (180.24bp,31.99bp) -- (180.64bp,31.11bp) -- (181.15bp,30.25bp) -- (181.79bp,29.41bp) -- (182.54bp,28.59bp) -- (183.42bp,27.8bp) -- (184.42bp,27.04bp) -- (185.53bp,26.31bp) -- (186.76bp,25.61bp) -- (188.1bp,24.94bp) -- (189.55bp,24.31bp) -- (191.11bp,23.71bp) -- (192.76bp,23.16bp) -- (194.51bp,22.65bp) -- (196.34bp,22.18bp) -- (198.26bp,21.75bp) -- (200.25bp,21.36bp) -- (202.31bp,21.03bp) -- (204.43bp,20.74bp) -- (206.59bp,20.49bp) -- (208.8bp,20.3bp) -- (211.04bp,20.15bp) -- (213.31bp,20.05bp) -- (215.59bp,20.0bp) -- (217.87bp,20.0bp) -- cycle;
                        \draw (216.73bp,38.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
                      \end{scope}
                        % Node: 3
                      \begin{scope}
                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
                        \pgfsetstrokecolor{strokecol}
                        \draw (316.46bp,34.0bp) ellipse (27.0bp and 18.0bp);
                        \draw (316.46bp,34.0bp) node {$\neg \text{a}$};
                      \end{scope}
                      %
%        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
        \caption{Timeline for %un-simplified
        $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
        \label{fig:unsimplified}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \resizebox{.8\textwidth}{!}{
            \begin{tikzpicture}[>=latex',line join=bevel,]
                \pgfsetlinewidth{1bp}
              %%
              \begin{scope}
                \pgfsetstrokecolor{black}
                \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
                \pgfsetstrokecolor{strokecol}
                \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
                \pgfsetfillcolor{fillcol}
